Surface programmable materials

### 2024-08-17 paper/main.tex
update

\subsubsection{Elementary cellular automaton}\label{elementary-cellular-automaton}

@@

\subsubsection{A 2D Surface Programmable Material}\label{a-2d-surface-programmable-material}

@@

\subsubsection{Non-deterministic
direction}\label{non-deterministic-direction}

Solving the ground state of the Hamiltonian of the Surface Programmable
Material is at least as hard as solving the circuit satisfiability
problem, which is NP-complete~\cite{Moore2011}.

@@

\subsection{Estimation of the computing
time}\label{estimation-of-the-computing-time}

>>>>

\section{Model and Method}
\subsection{Elementary cellular automaton}\label{elementary-cellular-automaton}

@@

\subsection{Energy Model}\label{a-2d-surface-programmable-material}

@@

Solving the ground state of the Hamiltonian of the Surface Programmable Material from the non-deterministic direction is at least as hard as solving the circuit satisfiability problem, which is NP-complete~\cite{Moore2011}.

@@

\subsubsection{Estimation of the computing time}\label{estimation-of-the-computing-time}
